\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-12 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Révision légère figure 1 et 2. Sortie des valeurs ...
Révision légère figure 1 et 2. Sortie des valeurs prédites total TC et beta

Signed-off-by: Guillaume Daudin <gdaudin@mac.com>
Guillaume sur le texte (surtout partie théorique)
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

Trade costs are central to international economic analysis. In particular, they are known to be a major obstacle to international economic integration and international trade flows. Defined as the costs associated with the exchange of goods across
national borders, trade costs are usually split between transaction costs, policy costs, time costs and transport costs \textit{per se}. Many argue that the latter have substantially decreased with technological advance in transportation, infrastructure development
and new communication technologies. However, several empirical evidence
suggest that transport costs remain large and deserve attention.\footnote{\cite{anderson_wincoop_jel} find that around 30\% of international trade costs are attributable to transport costs. Equivalently, international transportation costs represent a 21\% markup over production costs. Further, the sizable elasticity of trade with respect to freight costs obtained by \cite{Behar_Venables} (around -3) testifies to the impact of transport costs on trade flows. \cite{Disdier_Head08}, among others, point out that distance as an incompressible cost is still a very important determinant of trade flows.} In addition, progress in transportation techniques (which reduces the constant-dollar cost of transport) should be compared with technical progress in production (which reduces the constant-dollar cost of production) to get a clear picture of the evolution
of the transport costs burden. The latter also depends on whether the cost is in proportion of the value of goods traded (hence does not distort relative prices) or a cost per unit traded (the additive form conversely affecting relative prices). If a complex task, having a clear view of the international transport cost burden is of key importance, since the answers to several important (both academic and policy) economic issues depend in large part on how much distance-based costs affects trade, such as, among others, the dynamics of agglomeration, the profitability of outsourcing or the gains from trade liberalization. Our main contribution in this paper is to bring new insights on this matter.\smallskip

@@

On the theoretical side, we show the importance of embedding additive costs when assessing the effects of trade liberalization in normative terms. Specifically, we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction solely occurs through a decrease in the ad-valorem cost, as standardly modelled in New Trade theories, versus when it is achieved through a combined reduction in the ad-valorem and the additive components, as quantified by our empirical model. To this aim, we embed additive costs in the canonical \cite{melitz} model. Relying on our empirical estimates of transport costs
over 1974-2019, our preferred scenario shows an extra welfare gain by around 1.2 percentage point when the transport cost decrease encompasses a reduction in its additive component relative to a pure ad-valorem reduction. Put differently, neglecting additive costs thus leads to a substantial underestimation of the welfare gains of trade liberalisation.

@@

%Yet, our paper complements their findings in two main respects.
%In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed over the last fifty years.
%However, these papers yet do not allow for a quantitative measure of additive costs (neither for the ad-valorem costs). Another important contribution of this paper is to provide quantitative estimates of both type of transport costs. \smallskip
Our results are robust to a range of robustness checks, including the use of instrumental variables and more disaggregated data at the SITC 4 or HS10 levels. They have important implications for both international trade and international macroeconomics models. Some recent papers notably point out the normative implications of additive trade costs. \cite{sorensen2014} analytically shows that important welfare gains can be achieved by reducing additive trade costs. Not much progress has yet been made in quantifying such gains, one potential reason being the lack of an empirical characterization of the additive component of trade costs, the one exception being \citealp{Irrazabal_2015}. In contrast to them, we can exploit the time dimension of our database to quantify the welfare gains of the trade liberalization since 1974, based on our empirical yearly estimates over 1974-2019 of overall transport costs, as well as by sub-component (additive and ad-valorem).\smallskip

@@

Exploiting this dataset also has three advantages.
First, it comes from a single, homogenous and trustworthy customs source.
This limits the measurement error bias.
Based on customs declarations, the US Imports Database inventories all imports (both values and quantities), by country of origin, to the United States at the HS 10-digit level, with a concordance code to the SITC coding system. In addition, the database reports information regarding freight, insurance and handling expenditures by transportation mode, ocean (or ``vessel'') and air. We will make use of this to highlight potential differences in the magnitude of transport costs across transportation modes.
Second, this dataset provides both the import price and the export price for the same good (for a given origin country).
This is highly valuable, as it gives us a direct measure of international transport costs (at the country/sector level), from which we can estimate separately the levels of both the iceberg costs and of the additive costs, in contrast to e.g. \cite{Irrazabal_2015}.
Third, this dataset is available over a long time span, which enables us to analyze the trend patterns of international transport costs over the period 1974-2019.\footnote{Note that, as mentioned by \cite{Lafourcade_Thisse}, our transport costs measures are based on actual trade flows, i.e. ignoring those flows that did not happen because of presumably prohibitive transport costs.
In light of this, the estimated values that we obtain can be viewed as the lower bounds of the ``potential'' transport costs.} \smallskip

@@

As mentioned in the Introduction, one contribution of the paper is to provide a careful estimation of international transport costs, which decomposes into both an additive and an ad-valorem component. We do so by adopting the following strategy. For each year and transport mode, we estimate two models. In Model (A), additive costs are excluded, transport costs being modeled as iceberg costs only. In this case, the estimated equation simplifies as:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times\tau_{s(k)}-1 \right) + \epsilon^{ice}_{ik} \label{eq:model_nlI}
\end{equation}

@@

After estimating Equation (\ref{eq:model_IetA}), we can rebuild a measure of each component, $\widehat{\tau}^{adv}_{is(k)} = \widehat{\tau_{i}} \times \widehat{\tau}_{s(k)}$ for the ad-valorem cost and $\widehat{t}_{is(k)} = \widehat{t}_{i} + \widehat{t}_{s(k)}$ for the additive cost, that are country-sector specific, by year and transport mode.
When assuming iceberg costs only (Equation (\ref{eq:model_nlI})), we proceed similarly to get $\widehat{\tau}^{ice}_{is(k)} = \widehat{\tau}_{i} \times \widehat{\tau}_{s(k)}$.
In this case, notice that the equation could be estimated relying on a linear form.
To preserve comparability of the results, we keep the same non-linear estimation method in both cases.
Similarly, as \cite{Irrazabal_2015}, we take the average over the sector-country dimension, using the values of each trade flow ($is$-specific) over total yearly trade as a weighting scheme.
We thus recover a ``synthetic estimate'' of each type of transport cost: $\widehat{\tau}^{ice}$ for Model (A), $\widehat{\tau}^{adv}$ and $\widehat{t}$ for Model (B), for each year and transportation mode.
These results are reported in Section \ref{sec:results_decomposition}.

@@

@@

@@

The estimation carried out in section \ref{sec:results_decomposition} provides us with the
Starting from the additive and ad-valorem measures of international transport costs which vary over time, product and origin country (i.e., $\widehat{t}_{ikt}$ and $\widehat{\tau}_{ikt}$), we extract the pure transport cost measure by the mean of a time fixed effect.
Precisely, we extract the changes over time in the pure transport cost dimension by assuming a composition of trade flows by country partner and product that is constant throughout the period, and equal to the one observed in 1974. We conduct the same analysis on an overall transport costs measure, built by combining the two estimated components (additive and iceberg) in a unified measure of transport costs. The objective is to obtain six time series, all built as indices with the reference value 100 in 1974: three time series for the unfitted transport costs measures $\{\Gamma^{t/\widetilde{p}, raw}_t, \Gamma^{adv, raw}_t, \Gamma^{tc, raw}_t \}$, and three series for the fitted values $\{\Gamma^{t/\widetilde{p}}_t, \Gamma^{adv}_t, \Gamma^{tc}_t \}$ (additive, ad-valorem and total cost respectively).

@@

In this section, we explore the implications of our empirical results on theoretical grounds. Over the last decade, several papers examined the implications of non-iceberg costs. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment, and draw welfare conclusions regarding the variations of these costs. We have complemented these studies by providing a long-run characterization of both the additive and the multiplicative component of transports costs. In this section, we use our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two measures. One measure assumes that the reduction was achieved solely through the decline of ad-valorem costs, as modeled in standard New Trade theoretical approaches. The other measures builds on the results of our empirical investigation to assume that the reduction was achieved by a combined reduction in the ad-valorem and the additive components, as modeled by the addition of additive costs to the canonical \citet{melitz} model.\smallskip
%While the bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., iceberg trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation.

@@

%That said, it should be noted the case with additive costs in \cites{Lashkaripour_JIE2020}paper relies on a negligible share of additive costs. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} relies on a perfectly competitive environment,
Using a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}, as did \cite{sorensen2014} and \cite{Irrazabal_2015} makes a difference. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade liberalization lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Leaving aside the selection issue leads to an underestimation of the welfare gains that can be achieved by a reduction in additive transport costs.

@@

We are interested in studying the normative consequences of trade liberalization in presence or not of additive costs. To that aim, we will compare the equilibrium based on the values of transport costs at the beginning (1974) and at the very end of our estimation period (2019), in two seetings: one including only ad-valorem transport costs, and including both additive and ad-valorem costs. Besides, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. This can be captured in the model through a reduction in the fixed export cost $f_x$. Accordingly, we will assess the effects of the trade liberalization assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$.
%\footnote{We endogenously determine the initial value of $f_x$ such that the initial steady state (with 1974 values of transport costs) implies a share of exporting firms equal to 21\%, as in  \cite{ghironi} based on the value estimated by \cite{BEJK-AER-03} in the early 1990s. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 85\% (i.e., from 21\% to 39\%), based on the evidence reported in \cite{Lincoln_McCallum2018}, along with the 2019 values of variable transport costs xxxx GD redondant avec la note du tableau, non ?xxxx }

\subsection{Trade liberalization: The importance of additive costs}

Our empirical results point to two important conclusions: First, additive costs represent a non-negligible part of overall international transport costs. Second, total transport costs have strongly reduced over 1974-2019, and the decrease is particularly marked in the additive component in air transport. We exploit the theoretical implications of these empirical findings by running a comparative statics analysis following a reduction in variable transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario so-called \textit{à la Mélitz}, we assume that only ad-valorem costs apply. We hence apply the estimated reduction in total variable transport costs ``as if'' it was solely attributable to the ad-valorem component. In the second scenario so-called \textit{à la Hummels}, we rely on the estimates of transport costs involving both additive and ad-valorem components. The consequences of the reduction in international transport costs through both its additive and ad-valorem components.

In running this exercise, we also take into account the fact that the share of exporting firms has substantially increased since the 21\% value reported in \cite{BEJK-AER-03} (and consistent with the value estimated by \citet{Lincoln_McCallum2018} for 1987 on US data). According to \cite{Lincoln_McCallum2018}, this share roughly amounts to 39\% in the mid 2000s. This can be matched in the model by resetting the (lower) value of the export fixed cost $f_x$ accordingly. Our preferred scenario thus embeds the two dimensions of trade liberalization: the reduction of transport costs along with the reduction of the export fixed cost.

The results are reported in Table \ref{tab:resultats_modele}, panel (1), by transport mode (for Air (Columns (A)-(B)) and Vessel (Columns (C)-(D) respectively.\footnote{For sake of space saving, we only report the welfare consequences of trade liberalization, depending on the structure of transport costs, even if we refer to the positive effects (in terms of number of firms, threshold and average productivities, etc.) to explain the underlying mechanisms. The whole set of results is available upon request to the authors.} Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms.
We also simulate an alternative scenario where only the variable transport costs decrease, the fixed export cost being constant at its initial value. This has two purposes. It allows us to better highlight the specific mechanisms involved by a reduction in additive costs versus a reduction in ad-valorem costs. And it delivers a relevant robustness check on the welfare implications of additive costs. These results are reported in Table \ref{tab:resultats_modele}, panel (2).\footnote{Under a constant fixed export cost, we also compare two alternative cases. Starting from the values observed in 1974, we simulate \textit{(i)} the observed reduction in the additive cost $t/\widetilde{p}^{fas}$, maintaining the ad-valorem component at its initial (1974) value, and  \textit{(ii)} the opposite case, the observed reduction of ad-valorem costs ($\tau$), maintaining the additive component at its initial value. The quantitative results strongly confirm that, keeping cost level constant, additive costs are more detrimental for welfare than ad-valorem costs.
%, and the larger welfare gains when this specific component of international trade costs is reduced.
See Appendix \ref{app:theoretical_model}, Table \ref{tab:results_model_appendix} for the results}.

\begin{table}[htbp]
  \centering
  \caption{Trade liberalization: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c||c|c}
\hline
Mode & \multicolumn{2}{|c||}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
& (A) & (B) & (C) & (D)  \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-6.4 &-6.4   \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&-6.4&	-3.1	 \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-3.3 \\ \hline \hline
\multicolumn{4}{l}{(1) Lower fixed export cost} \\ \hline
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 	\textbf{2.50}	&\textbf{3.16}	&	\textbf{3.63}&	\textbf{4.26 }  \\\hline
Variety effect (\%)&1.36 &0.48	&-0.43	&-1.28 \\
Price effect (\%)&	1.14 &	2.66&		 4.08&	5.63 \\ \hline \hline
\multicolumn{4}{l}{(2) Constant fixed export cost} \\ \hline
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.23&	2.18 & 2.39	&3.38 	 \\ \hline
Variety effect (\%)& -0.83 	&-1.32	&-2.60	& -3.12 \\
Price effect (\%)&2.08 &3.56	&5.20	& 6.83  \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{10cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. In Columns B and D, we first simulate the observed reduction in $\tau$ and iterate on the reduced value of $t$ such that the simulated value of $t/\widetilde{p}_x^{\text{fas}}$ matches the empirical target.  }}}
\end{table}

>>>>

Trade costs are central to international economic analysis. In particular, they are known to be a major obstacle to international economic integration and international trade flows. Defined as the costs associated with the exchange of goods across
national borders, trade costs are usually split between transaction costs, policy costs, time costs and transport costs \textit{per se}. Many argue that the latter have substantially decreased with technological advance in transportation, infrastructure development
and new communication technologies. However, several empirical evidence
suggest that transport costs remain large and deserve attention.\footnote{\cite{anderson_wincoop_jel} find that around 30\% of international trade costs are attributable to transport costs. Equivalently, international transportation costs represent a 21\% markup over production costs. Further, the sizable elasticity of trade with respect to freight costs obtained by \cite{Behar_Venables} (around -3) testifies to the impact of transport costs on trade flows. \cite{Disdier_Head08}, among others, point out that distance as an incompressible cost is still a very important determinant of trade flows.} In addition, progress in transportation techniques (which reduces the constant-dollar cost of transport) should be compared with technical progress in production (which reduces the constant-dollar cost of production) to get a clear picture of the evolution
of the transport costs burden. The latter also depends on whether the cost is in proportion of the value of goods traded (hence does not distort relative prices) or a cost per unit traded (the additive form conversely affecting relative prices). If a complex task, having a clear view of the international transport cost burden is of key importance, since the answers to several important (both academic and policy) economic issues depend in large part on how much distance-based costs affects trade, such as, among others, the dynamics of agglomeration, the profitability of outsourcing or the gains from trade cost reduction. Our main contribution in this paper is to bring new insights on this matter.\smallskip

@@

On the theoretical side, we show the importance of embedding additive costs when assessing the effects of trade cost reduction in welfare terms. Specifically, we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction solely occurs through a decrease in the ad-valorem cost, as standardly modelled in New Trade theories, versus when it is achieved through a combined reduction in the ad-valorem and the additive components, as quantified by our empirical model. To this aim, we embed additive costs in the canonical \cite{melitz} model. Relying on our empirical estimates of transport costs
over 1974-2019, our preferred scenario shows an extra welfare gain by around 1.2 percentage point when the transport cost decrease encompasses a reduction in its additive component relative to a pure ad-valorem reduction. Put differently, neglecting additive costs thus leads to a substantial underestimation of the welfare gains of trade liberalisation.

@@

%Yet, our paper complements their findings in two main respects.
%In particular, we show that the modeling of additive costs is of critical importance in determining the underlying sources of the trends patterns of international transport costs observed over the last fifty years.
%However, these papers yet do not allow for a quantitative measure of additive costs (neither for the ad-valorem costs). Another important contribution of this paper is to provide quantitative estimates of both type of transport costs. \smallskip
Our results are robust to a range of robustness checks, including the use of instrumental variables and more disaggregated data at the SITC 4 or HS10 levels. They have important implications for both international trade and international macroeconomics models. Some recent papers notably point out the welfare implications of additive trade costs. \cite{sorensen2014} analytically shows that important welfare gains can be achieved by reducing additive trade costs. Not much progress has yet been made in quantifying such gains, one potential reason being the lack of an empirical characterization of the additive component of trade costs, the one exception being \citealp{Irrazabal_2015}. In contrast to them, we can exploit the time dimension of our database to quantify the welfare gains of the trade cost reduction since 1974, based on our empirical yearly estimates over 1974-2019 of overall transport costs, as well as by sub-component (additive and ad-valorem).\smallskip

@@

Exploiting this dataset also has three advantages.
First, it comes from a single, homogenous and trustworthy customs source.
This limits the measurement error bias.
Based on customs declarations, the US Imports Database inventories all imports (both values and quantities), by country of origin, to the United States at the HS 10-digit level, with a concordance code to the SITC coding system. In addition, the database reports information regarding freight, insurance and handling expenditures by transportation mode, ocean (or ``vessel'') and air. We will make use of this to highlight potential differences in the magnitude of transport costs across transportation modes.
Second, this dataset provides both the import price and the export price for the same good (for a given origin country).
This is highly valuable, as it gives us a direct measure of international transport costs (at the country/sector level), from which we can estimate separately the levels of both the ad-valorem costs and of the additive costs, in contrast to e.g. \cite{Irrazabal_2015}.
Third, this dataset is available over a long time span, which enables us to analyze the trend patterns of international transport costs over the period 1974-2019.\footnote{Note that, as mentioned by \cite{Lafourcade_Thisse}, our transport costs measures are based on actual trade flows, i.e. ignoring those flows that did not happen because of presumably prohibitive transport costs.
In light of this, the estimated values that we obtain can be viewed as the lower bounds of the ``potential'' transport costs.} \smallskip

@@

As mentioned in the Introduction, one contribution of the paper is to provide a careful estimation of international transport costs, which decomposes into both an additive and an ad-valorem component. We do so by adopting the following strategy. For each year and transport mode, we estimate two models. In Model (A), additive costs are excluded, transport costs being modeled as ad-valorem costs only. In this case, the estimated equation simplifies as:
\begin{equation}
\ln\left(\frac{p_{ik}}{\widetilde{p}_{ik}}-1 \right)= \ln \left(\tau_{i}\times\tau_{s(k)}-1 \right) + \epsilon^{ice}_{ik} \label{eq:model_nlI}
\end{equation}

@@

After estimating Equation (\ref{eq:model_IetA}), we can rebuild a measure of each component, $\widehat{\tau}^{adv}_{is(k)} = \widehat{\tau_{i}} \times \widehat{\tau}_{s(k)}$ for the ad-valorem cost and $\widehat{t}_{is(k)} = \widehat{t}_{i} + \widehat{t}_{s(k)}$ for the additive cost, that are country-sector specific, by year and transport mode.
When assuming ad-valorem costs only (Equation (\ref{eq:model_nlI})), we proceed similarly to get $\widehat{\tau}^{ice}_{is(k)} = \widehat{\tau}_{i} \times \widehat{\tau}_{s(k)}$.
In this case, notice that the equation could be estimated relying on a linear form.
To preserve comparability of the results, we keep the same non-linear estimation method in both cases.
Similarly, as \cite{Irrazabal_2015}, we take the average over the sector-country dimension, using the values of each trade flow ($is$-specific) over total yearly trade as a weighting scheme.
We thus recover a ``synthetic estimate'' of each type of transport cost: $\widehat{\tau}^{ice}$ for Model (A), $\widehat{\tau}^{adv}$ and $\widehat{t}$ for Model (B), for each year and transportation mode.
These results are reported in Section \ref{sec:results_decomposition}.

@@

%%Sur le trend :      +------------------------------+
%| trend_~t         mode   year |
%|------------------------------|
%1. | 3.652468   (b) Vessel   2019 |
%46. | 8.546226   (b) Vessel   1974 |
%47. | 2.488636      (a) Air   2019 |
%92. | 6.289694      (a) Air   1974 |
%+------------------------------+

@@

%Le beta sur le trend quadratic (  reg ln_meanshareA year year2 )
%
%   +------------------------------+
%| trend_~a         mode   year |
%|------------------------------|
%1. |  .438216   (b) Vessel   2019 |
%46. | .3468959   (b) Vessel   1974 |
%47. | .2301836      (a) Air   2019 |
%92. | .3839365      (a) Air   1974 |
%+------------------------------+
%))

@@

The estimation carried out in section \ref{sec:results_decomposition} provides us with the
Starting from the additive and ad-valorem measures of international transport costs which vary over time, product and origin country (i.e., $\widehat{t}_{ikt}$ and $\widehat{\tau}_{ikt}$), we extract the pure transport cost measure by the mean of a time fixed effect.
Precisely, we extract the changes over time in the pure transport cost dimension by assuming a composition of trade flows by country partner and product that is constant throughout the period, and equal to the one observed in 1974. We conduct the same analysis on an overall transport costs measure, built by combining the two estimated components (additive and ad-valorem) in a unified measure of transport costs. The objective is to obtain six time series, all built as indices with the reference value 100 in 1974: three time series for the unfitted transport costs measures $\{\Gamma^{t/\widetilde{p}, raw}_t, \Gamma^{adv, raw}_t, \Gamma^{tc, raw}_t \}$, and three series for the fitted values $\{\Gamma^{t/\widetilde{p}}_t, \Gamma^{adv}_t, \Gamma^{tc}_t \}$ (additive, ad-valorem and total cost respectively).

@@

In this section, we explore the implications of our empirical results on theoretical grounds. Over the last decade, several papers examined the implications of non-ad-valorem costs. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment, and draw welfare conclusions regarding the variations of these costs. We have complemented these studies by providing a long-run characterization of both the additive and the multiplicative component of transports costs. In this section, we use our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two measures. One measure assumes that the reduction was achieved solely through the decline of ad-valorem costs, as modeled in standard New Trade theoretical approaches. The other measures builds on the results of our empirical investigation to assume that the reduction was achieved by a combined reduction in the ad-valorem and the additive components, as modeled by the addition of additive costs to the canonical \citet{melitz} model.\smallskip
%While the bulk of the trade literature investigates the role of trade costs modelled as ad-valorem costs (e.g., ad-valorem trade costs), not much is said about the role of the additive component. One potential explanation is the lack of empirical estimates about the size of additive costs. Our results may thus usefully palliate this limitation.

@@

%That said, it should be noted the case with additive costs in \cites{Lashkaripour_JIE2020}paper relies on a negligible share of additive costs. In this context, one might expect that whether additive costs are present or not makes little difference. As underlined by \cite{Lashkaripour_JIE2020}, a second explanation may rely on the modeling framework. While \cite{Lashkaripour_JIE2020} relies on a perfectly competitive environment,
Using a model with monopolistic competition and firm selection \`{a} la \cite{melitz} or \cite{chaney2008}, as did \cite{sorensen2014} and \cite{Irrazabal_2015} makes a difference. In this setting, we show that additive costs do modify the selection of firms on both the domestic and the export markets, e.g the extensive margin of trade, whose role in the welfare gains of trade cost reduction lies at the heart of the New Trade models  \`{a} la \cite{melitz}. Leaving aside the selection issue leads to an underestimation of the welfare gains that can be achieved by a reduction in additive transport costs.

@@

We are interested in studying the welfare consequences of trade cost reduction in presence or not of additive costs. To that aim, we will compare the equilibrium based on the values of transport costs at the beginning (1974) and at the very end of our estimation period (2019), in two seetings: one including only ad-valorem transport costs, and including both additive and ad-valorem costs. Besides, \cite{Lincoln_McCallum2018} document the large increase in the number of exporting firms in the US between the mid 1980s et the mid 2000s, with a share of exporting firms raising by 52\% over this period. This can be captured in the model through a reduction in the fixed export cost $f_x$. Accordingly, we will assess the effects of the trade cost reduction assuming a joined reduction in both the variable transport costs ($\tau, t$, based on our empirical estimates) and the fixed export cost $f_x$.
%\footnote{We endogenously determine the initial value of $f_x$ such that the initial steady state (with 1974 values of transport costs) implies a share of exporting firms equal to 21\%, as in  \cite{ghironi} based on the value estimated by \cite{BEJK-AER-03} in the early 1990s. In the final steady state, $f_x$ will be revealed such that this share of exporting plants has increased by 85\% (i.e., from 21\% to 39\%), based on the evidence reported in \cite{Lincoln_McCallum2018}, along with the 2019 values of variable transport costs xxxx GD redondant avec la note du tableau, non ?xxxx }

\subsection{Trade cost reduction: The importance of additive costs}

Our empirical results point to two important conclusions: First, additive costs represent a non-negligible part of overall international transport costs. Second, total transport costs have strongly reduced over 1974-2019, and the decrease is particularly marked in the additive component in air transport. We exploit the theoretical implications of these empirical findings by running a comparative statics analysis following a reduction in variable transport costs based on our estimates in 1974 and 2019, by transport mode. Specifically, we contrast two cases: In the first scenario, we assume that only ad-valorem costs apply. We hence apply the estimated reduction in total variable transport costs ``as if'' it was solely attributable to the ad-valorem component. In the second scenario, we rely on the estimates of transport costs involving both additive and ad-valorem components. The consequences of the reduction in international transport costs through both its additive and ad-valorem components.

In running this exercise, we also take into account the fact that the share of exporting firms has substantially increased since the 21\% value reported in \cite{BEJK-AER-03} (and consistent with the value estimated by \citet{Lincoln_McCallum2018} for 1987 on US data). According to \cite{Lincoln_McCallum2018}, this share roughly amounts to 39\% in the mid 2000s. This can be matched in the model by resetting the (lower) value of the export fixed cost $f_x$ accordingly. Our preferred scenario thus embeds the two dimensions of trade cost reduction: the reduction of transport costs along with the reduction of the export fixed cost.

The results are reported in Table \ref{tab:resultats_modele}, panel (1), by transport mode (for Air (Columns (A)-(B)) and Vessel (Columns (C)-(D) respectively.\footnote{For sake of space saving, we only report the welfare consequences of trade cost reduction, depending on the structure of transport costs, even if we refer to the positive effects (in terms of number of firms, threshold and average productivities, etc.) to explain the underlying mechanisms. The whole set of results is available upon request to the authors.} Specifically, we report the change in total transport costs (expressed in percentage points, and based on the raw numbers reported in Table \ref{tab:calib_TC}), decomposed in its two dimensions (additive and ad-valorem); as well as the welfare change, both in absolute and in relative terms.
We also simulate an alternative scenario where only the variable transport costs decrease, the fixed export cost being constant at its initial value. This has two purposes. It allows us to better highlight the specific mechanisms involved by a reduction in additive costs versus a reduction in ad-valorem costs. And it delivers a relevant robustness check on the welfare implications of additive costs. These results are reported in Table \ref{tab:resultats_modele}, panel (2).\footnote{Under a constant fixed export cost, we also compare two alternative cases. Starting from the values observed in 1974, we simulate \textit{(i)} the observed reduction in the additive cost $t/\widetilde{p}^{fas}$, maintaining the ad-valorem component at its initial (1974) value, and  \textit{(ii)} the opposite case, the observed reduction of ad-valorem costs ($\tau$), maintaining the additive component at its initial value. The quantitative results strongly confirm that, keeping cost level constant, additive costs are more detrimental for welfare than ad-valorem costs.
%, and the larger welfare gains when this specific component of international trade costs is reduced.
See Appendix \ref{app:theoretical_model}, Table \ref{tab:results_model_appendix} for the results}.

\begin{table}[htbp]
  \centering
  \caption{Trade cost reduction: The role of additive costs} \label{tab:resultats_modele}
\begin{center}
\begin{tabular}{l||c|c||c|c}
\hline
Mode & \multicolumn{2}{|c||}{Air} & \multicolumn{2}{c}{Vessel} \\ \hline
& (A) & (B) & (C) & (D)  \\
Reduction in: & $\tau$ only & $\tau$ and $t$ &$\tau$ only & $\tau$ and $t$\\  \hline
%$TC_{1974}$ & 0.062 & 0.062 & 0.062 & 0.062 & 0.105 & 0.105 & 0.105 & 0.105\\
%$TC_{2019}$ &  0.028 & 0.028 & 0.028 & 0.028&  0.041 & 0.041 & 0.041 & 0.041\\
$\Delta TC$ (in pp) &-3.4 &-3.4 &-6.4 &-6.4   \\
$\Delta \tau$ (in pp) & -3.4	&-1.4&-6.4&	-3.1	 \\
$\Delta t/\widetilde{p}_x^{\text{fas}}$ (in pp) & 0&	-2.0&	0&	-3.3 \\ \hline \hline
\multicolumn{4}{l}{(1) Lower fixed export cost} \\ \hline
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 	\textbf{2.50}	&\textbf{3.16}	&	\textbf{3.63}&	\textbf{4.26 }  \\\hline
Variety effect (\%)&1.36 &0.48	&-0.43	&-1.28 \\
Price effect (\%)&	1.14 &	2.66&		 4.08&	5.63 \\ \hline \hline
\multicolumn{4}{l}{(2) Constant fixed export cost} \\ \hline
$\Delta \mathcal{W}/\mathcal{W}$ (in \%) & 1.23&	2.18 & 2.39	&3.38 	 \\ \hline
Variety effect (\%)& -0.83 	&-1.32	&-2.60	& -3.12 \\
Price effect (\%)&2.08 &3.56	&5.20	& 6.83  \\
\hline
\end{tabular}
\end{center}
{\parbox[l]{10cm}{ \vspace{4pt}\footnotesize{Notes: TC = Transport Costs, expressed in percentage of the average export fas price. The reduction in transport costs is expressed in percentage points. In Columns B and D, we first simulate the observed reduction in $\tau$ and iterate on the reduced value of $t$ such that the simulated value of $t/\widetilde{p}_x^{\text{fas}}$ matches the empirical target.  }}}
\end{table}

\textbf{Inverser panel 1 et 2 pour avoir le même ordre dans le tableau et le texte xxxxGD}
In line with the literature, we find that a reduction of trade costs  induces welfare gains
% whatever the transport mode (and the associated magnitude of the transport costs decrease).
The originality of our results rather dwells on comparing the welfare gains depending on the type of cost reduction.
Welfare gains are higher when the trade cost reduction includes a decrease in additive trade costs.
This is consistent with the analytical results of \cite{sorensen2014} and the quantitative ones of \cite{Irrazabal_2015}.
%in a different exercise of trade cost reduction though. \footnote{\cite{sorensen2014} compares the welfare effect of a trade costs reduction depending whether it is exclusively ad-valorem or exclusively additive, the comparison between both trade cost decreases being a criterion of equal impact on trade openness. Our quantitative model offers a more general and flexible set-up, as we can virtually consider all cases of trade cost reduction. Based on our empirical estimates, we compare the effects of the same decrease in overall transport costs depending on 1) whether additive costs are present or not, and 2) when they are present, assuming that the trade cost decrease is achieved by a reduction of both additive and ad-valorem components.}
Quantitatively, the welfare gains are sizeable. In our preferred scenario, the reduction in variable transport costs generates a relative welfare gain higher by around 25\% percentage point when such a reduction occurs through the additive component (which accounts for 50 to 60\% of the total cost decrease, depending on the transport mode), rather than when it realizes through a decrease in ad-valorem costs only (Table \ref{tab:resultats_modele}, panel (1), Column (B) vs (A) for Air, (D) vs (C) for Vessel). xxxGD ajuster avec les nouveaux chiffresxxx.
%Closely related to our work, \cite{Irrazabal_2015} also quantify the welfare losses of imposing trade taxes depending on whether they are additive or ad-valorem. If we share a similar conclusion regarding the importance of additive costs, our empirical analysis allows us to simulate the effects of the reduction in transport costs actually observed in the data over the period 1974-2019, in all their dimensions (additive and ad-valorem).
\smallskip
